The development of abstract concepts in the early lexical network

### 2019-02-25 CMCL/ms.Rmd

---
title: "How to Make a Camera-Ready Proceedings Contribution"

@@

abstract: 
    "This document contains the instructions for preparing a camera-ready
  manuscript for the proceedings of EACL-2017. The document itself
  conforms to its own specifications, and is therefore an example of
  what your manuscript should look like. These instructions should be
  used for both papers submitted for review and for final versions of
  accepted papers.  Authors are asked to conform to all the directions
  reported in this document."

@@

```{r, libraries}
library(png)
library(dplyr)
library(ggplot2)
library(grid)
library(lme4)
library(lmerTest)
library(ggthemes)
library(ggplot2)
library(xtable)
```

# Methods

##Nouns 
We used data from Wordbank (Frank et al., 2017), an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist, Toddler version. Parent report is a reliable and valid measure of children's vocabulary (Fenson et al., 1994). We used a set of nouns representing hand-checked translation equivalents  across 10 languages (available in Wordbank database). We "assume" (i should ask what were the criteria for the unilemma selection) that this set of translation equivalents is representative of a core shared vocabulary across all children (in different cultures) by around 30 months, 
<!--and we study possible cross-lingusitic variation in the way this shared knowledge is arrived at in development. -->

The conceptual organization derived from this shared vocabulary is obviousely identical across languages, but we investigate whether there are systematic cross-lingusitc variations in the order of aquisition of words that make up this vocabulary, and crucially, whether such variation influences the induced conceptual organization at different points in time. In fact, differences in the order of acqusition of words do not necessarily give rise to different conceptual organization. Imagine that two languages vary in whether "cow" or "dog" is acquired first. This difference will not change the induced conceptual organization across time since both "dog" and "cow" are instances of the same high-level concept "animal".

```{r fig.env = "figure", fig.pos = "h", fig.align = "center", set.cap.width=T, fig.width=4, fig.height=3, num.cols.cap=2, fig.cap = "bla bla"}

@@

ggplot(cor_all, 
      aes(x = tau, fill=data)) +
  geom_histogram(aes(y = (..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
                 alpha=0.5,
                 binwidth=0.05)+
  #scale_x_log10() +
  theme_few() + 
  theme(aspect.ratio = 0.7, legend.title = element_text(size=8)) +  #facet_grid(Segmentation ~ language)+
  scale_y_continuous(labels = scales::percent)+
  xlab("pairwise correlation") +ylab("Count")

@@

## Features
We used two sources of information which represent two ways words may be related to one another in the semantic network. The first source was the MacRae features (McRae et al., 2005). These features were collected by giving adult participants a set of nouns and prompting them to provide various kinds of properties (perceptual, functional, encyclopedic, and taxonomic). We followed Hills et al. 2010 in excluding the encyclopedic and taxonomic properties as their role may not be important at this stage of development. The other source was the semantic similarity derived based on co-occurrence in the corpus of CHILDES, using word2vec.

##Network 
We constructed networks using CDI words as nodes. Pairs of words were linked by an edge weighted by the number of shared MacRae feature or with the continuous distance obtained via Word2vec.  To model change in the conceptual organization from month to month, we constructed a different network at each month, based on the words that have been acquired by that month. We defined the age of acquisiton of a given word by the month at which this noun was produced by at least 50% of children, in each language (Goodman et al., 2008).

## Small World properties
We test whether the networks display the so-called "small-world" properties similar to other semantic and real-world networks (Steyvers & Tenenbaum, 2005; Watts & Strogatz, 1998). Small world properties are characterized with the average clustering coefficient $C$ and the average shortest path $L$. The former measures the extent to which the network is clustered, i.e., made of highly connectned sub-networks, whereas the latter measures the typical separation between tow nodes in the network. A network is small-word if it has a higher clustering coeffient comapred to a randomly connected network of the same size $C \gg C_{random}$, while still having a shorest path length as small as the one typically observed in random networks, that is $L \approx L_{random}$.

```{r fig.env = "figure*", fig.pos = "h", fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.width=7, fig.height=14, fig.cap = "bla bla"}
measurements <- readRDS("data/measurements.rds")

all <- measurements %>%
  filter(measure %in% c("pair_precision_to_last", "pair_recall_to_last"),
         randomization != "to_nearest_aoa") #%>%
  #group_by(n_clusters, age, measure, randomization) %>%
  #summarise(mean = mean(value))

all_sum <- all %>%
  group_by(measure, randomization, age) %>%
  summarise(myMean = mean(value, na.rm = TRUE))

ggplot(data=all, aes(x=age, y=value, col=randomization)) +
  #geom_point() +
  geom_smooth(method="lm", formula = y ~ poly(x, 3)) +
  #geom_smooth(method="lm", formula = y ~ log(x)) +
  theme_few() + 
  theme(aspect.ratio = 0.7)+
  facet_grid(.~measure)
```
## Clustering analysis
We identified network clusters using WalkTrap (Pons & Latapy, 2006), a community detection algorithm based on the fact that a random walker tends to be trapped in dense parts of a network corresponding to highly interconnected sub-groups of nodes.

## Evaluation of clusterings aross development
We note $\mathcal{C}_t$ the clustering at month $t$, based on the subset of the vocabulary acquired by that month in each language. The evaluation consists in comparing $\mathcal{C}_t$ to the final clustering $\mathcal{C}^*$ obtained using the full vocabulary by the last month of acquisition (i.e., $\mathcal{C}^*$=$\mathcal{C}_t$ for $t$=30 months). Such comparison allows us to study how words acquired at different points in time may induce changes in the conceptual organization. In addition, we investigate consistency and variability in this change across languages.

We compare $\mathcal{C}_t$ to $\mathcal{C}^*$ using a standard method in clustering comparison, which is based on counting word pairs on which the two clusterings agree or disagree (Rand, 1971; Hubert and Arabie, 1985). A pair of words learned by month $t$ can fall under one of the four follwoing cases: 1) pairs that are placed in the same cluster under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$ (True positives, noted as $tp(\mathcal{C}_t)$), 2) pairs placed in different clsuters under $\mathcal{C}_t$ and in different clusters under $\mathcal{C}^*$ (True negatives, $tn(\mathcal{C}_t)$), 3) pairs placed in the same cluster under $\mathcal{C}_t$ and in different clusters under $\mathcal{C}^*$ (False positive, $fp(\mathcal{C}_t)$), and 4) pairs placed in different clusters under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$ (False negatives, $fn(\mathcal{C}_t)$).

The clustering precison $P(\mathcal{C}_t)$ and recall $R(\mathcal{C}_t)$ are defiend as follows:

$$
P(\mathcal{C}_t) = \frac{|tp(\mathcal{C}_t)|}{|tp(\mathcal{C}_t)| + |fp(\mathcal{C}_t)|}
$$
$$
R(\mathcal{C}_t) = \frac{|tp(\mathcal{C}_t)|}{|tp(\mathcal{C}_t)| + |fn(\mathcal{C}_t)|}
$$
Both Precison and Recall converge to 1 (perfect score) as $\mathcal{C}_t$ becomes more and more similar to $\mathcal{C}^*$. If precision starts low before converging to 1 (as opposed to being a constant at 1), this pattern would indicate that some pairs that should be differentiated are initially lumped together, suggesting a process of "differentiation" over development. Similarly, if we observe an increase in Recall, this pattern would indicate that some pairs that should be associated are initially differentiate, suggesting a process of "coelescence" over development.

## Word ordering 
The question we are addressing is whether the order of acqusition of words affect the

#Results

@@

<!--
If precision is lower early on, it means that initial concepts are not differentiated enough, that is, pairs that should belong to different concpets are intially lamped together (false positives), despite the fact that we forced the same number of clsuters in both $\mathcal{C}_t$ and $\mathcal{C}^*$ (Why is this the case? This looks like an artefact of the clustering algorithm with smaller size data? Should discuss this with Isaac. Also, what is an exmaple of a clustering $\mathcal{C}_t$ for a smaller size: are some clusters totally empty?)

>>>>

---
title: "The development of abstract concepts in the early lexical network"

@@

abstract: 
    "How do children learn abstract concepts such as animal vs. artefact? Previous research suggests that such concepts can be derived using cues from the language they hear around them, e.g., word co-occurrence.  We propose that such information can be integrated in the evolving lexical network, and higher-level organization can be identified bottom-up as the dense components in this network. We found that early abstract categories develop simultaneously thanks to the children's word trajectory which favors the exploration of the global conceptual space."

@@

```{r, libraries}
library(png)
library(dplyr)
library(plyr)
library(broom)
#library(tidyr)
library(purrr)
library(langcog)
library(ggplot2)
library(grid)
library(lme4)
library(lmerTest)
library(ggthemes)
library(ggplot2)
library(xtable)
```

#Introduction:
<!--Different factors influence word learning. But here we are interested in how this order may influnce conceptual development
-The role of language is particularly important in the acquisition of higher levels concepts (because shared features are not necessarily perceived). One idea is to used the way words are distributed in child directed speech to infer the underlying categories

Concepts are the building blocks of ideas. For example, the thought "birds are animals" requires the knowledge of both the concept "birds" and the concept "animal". They enable inductive reasoning and predictive inferences which guide behavior and explanation (Murphy, 2002). 
-->
One of the central challenges in cognitive development is to understand how concepts develop \cite{carey2009,keil1992,gopnik1997}. Of particular interest is the case of abstract concepts which have non-obvious shared properties such as "animal" and "artefacts". For example, a cat and a bird are perceptually quite different but they share some fundamental properties (e.g., breathing, feeding, and reproducing) which make them animals, and which set them apart from  the category of artefacts. In such cases learning requires, at least in part, cultural/linguistic cues which provide information beyond what can be obtained through the senses \cite{gelman2009,harris2012,csibra2009}

One way children's conceptual learning can benefit from the language they hear around them is through word co-occurrence. For example, one can learn an abstract concept (e.g., animal) simply by observing how its instances (e.g., "cat" and "bird") go together in speech. This is a plausible learning strategy. On the one hand, experimental research has shown that children track co-occurrence statistics \cite{saffran1996}. On the other hand, inspection of the caregiver’s input shows that it contains rich co-occurrence information about various abstract concepts \cite{huebner2018}.

What remains to be investigated is the way abstract concepts develop from the interaction of the children's learning mechanisms and the structure of their linguistic input. We study this development and compare it to two hypothetical developmental scenarios. On the first, learning starts by exploring the global conceptual structure; categories are refined simultaneously over development (we call this mechanism exploration-based learning). On the second scenario, learning starts by exploring a small region of the conceptual space (e.g., the category "animals") and only after the refinement of this category, does the learner move to another (we call this mechanism exploitation-based learning).

The paper is organized as follows. First we describe the research strategy. In brief, we represented the developing lexicon as an evolving network and we used word co-occurrence in parent speech as a measure of words' relatedness. We operationalized high-level concepts as the highly interconnected components of the network.  Second, we explore how the pattern of children's word learning influences higher-level conceptual development, and we compare this pattern to the development induced by the exploration-based and exploitation-based mechanisms. Finally, we discuss the findings in light of previous research.

```{r network, fig.env = "figure*", fig.pos = "h", fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.width=5, fig.height=8, fig.cap = "Network obtained using a sample of nouns in CDI data (nodes), and co-occurrence-based similarity from a corpus of child-directed speech (edges). Colors indicate highly interconnected clusters identified using unsupervised network community detection. The clusters correspond, overall, to four higher-level concepts: animal, food, clothes, and artefacts."}

img <- png::readPNG("figs/graph.png")
grid::grid.raster(img)

# Data and Methods

## Constructing lexical networks

The networks' nodes were nouns form  Wordbank \cite{frank2017}, an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist, Toddler version \cite{fenson94}. Pairs of nouns were linked by weighted edges representing their semantic similarity derived based on co-occurrence in the corpus of child directed speech CHILDES \cite{macwhinney2014}, using Word2Vec algorithm \cite{mikolov2013}.

First, we constructed the end-state network based on a subset of CDI data. This subset was made of nouns belonging to a diversity of semantic categories. Items of this subset (named "uni_lemmas" in the WordBank database) were translated across the languages used in this study, allowing us to account for cross-linguistic variability. Second, to study development towards the end-state, we constructed a different network at each month, based on the nouns that have been learned by that month.

## Identifying high-level concepts in a network

We assume that high-level concepts correspond to clusters of highly interconnected nodes in the networks. We identified such clusters using  WalkTrap \cite{pons2006}, an unsupervised community detection algorithm based on the fact that a random walker tends to be trapped in dense parts of a network. Figure \ref{fig:network} shows the outcome of cluster identification in the end-state network. The algorithm obtained four major clusters corresponding to the categories of clothes, food, animal and artefacts. We refer to this end-state clustering as $\mathcal{C}^*$. To examine developmental change in the conceptual organization, we run the cluster identification algorithm at each month of acquisition $t$, and we compare the resulting clustering, noted $\mathcal{C}_t$, to that of the end-state $\mathcal{C}^*$. The method of this comparison is detailed below.

```{r results, fig.env = "figure*", fig.pos = "h", fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.width=7, fig.height=3, fig.cap = "Mean precision and recall scores obtained through comparing the end-state clustering to clusterings at different months of acquisition, across different languages. Colors indicates real and hypothetical word sampling mechanisms. Errors bars represent 95\\% confidence intervals."}

measurements <- readRDS("data/measurements.rds")

all <- measurements %>%
  filter(measure %in% c("pair_precision_to_last", "pair_recall_to_last"),
         randomization != "to_nearest_aoa",
         n_clusters != '5') #%>%
  #group_by(n_clusters, age, measure, randomization) %>%
  #summarise(mean = mean(value))

all_sum <- all %>%
  group_by(measure, randomization, age) %>%
  multi_boot_standard(col = "value", na.rm = TRUE)
  #summarise(myMean = mean(value, na.rm = TRUE))

all_sum$measure <- mapvalues(all_sum$measure, from = c("pair_precision_to_last", "pair_recall_to_last"), to = c("Precision", "Recall"))
all_sum$randomization <- mapvalues(all_sum$randomization, from = c("none", "random_aoa", "within_last_clustering"), to = c("Real", "Exploration","Exploitation"))

all_sum$randomization <- factor(all_sum$randomization, levels = c("Real", "Exploration","Exploitation"))

ggplot(data=all_sum, aes(x=age, y=mean, col=randomization)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1),
                  size=0.1)+
  geom_line()+
  xlab("Age") + ylab("Mean score") +
  #geom_smooth(method="lm", formula = y ~ poly(x, 3)) +
  #geom_smooth(method="lm", formula = y ~ log(x)) +
  theme_few() + 
  theme(aspect.ratio = 0.7,
        legend.title = element_blank())+
  facet_grid(.~measure) +
  theme(legend.position="bottom")
```

## Measuring conceptual development

We measure conceptual development by comparing $\mathcal{C}_t$ to $\mathcal{C}^*$ across time. We used a standard method in clustering comparison, which is based on counting word pairs on which the two clusterings agree or disagree \cite{rand1971,hubert1985}. A pair of words learned by month $t$ can fall under one of the four following cases:

\begin{enumerate}

  \item True positives $tp(\mathcal{C}_t)$: pairs that are placed in the same cluster under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$.
  \item True negatives $tn(\mathcal{C}_t)$: pairs placed in different clusters under $\mathcal{C}_t$ and in different clusters under $\mathcal{C}^*$.
  \item False positive $fp(\mathcal{C}_t)$: pairs placed in the same cluster under $\mathcal{C}_t$ and in different clusters under $\mathcal{C}^*$.
  \item False negatives $fn(\mathcal{C}_t)$: pairs placed in different clusters under $\mathcal{C}_t$ and in the same cluster under $\mathcal{C}^*$.

\end{enumerate}

We quantify clustering comparison using precision $P(\mathcal{C}_t)$ and recall $R(\mathcal{C}_t)$, defined as follows:

$$
P(\mathcal{C}_t) = \frac{|tp(\mathcal{C}_t)|}{|tp(\mathcal{C}_t)| + |fp(\mathcal{C}_t)|}
$$

$$
R(\mathcal{C}_t) = \frac{|tp(\mathcal{C}_t)|}{|tp(\mathcal{C}_t)| + |fn(\mathcal{C}_t)|}
$$
We made this comparison using different degrees of clustering granularity. More precisely, we fixed the same number of clusters for both $\mathcal{C}_t$ and $\mathcal{C}^*$, and we varied this number from two to four clusters. We did not use the trivial case of one cluster, nor did we did use more than four clusters, since this number was optimal for the largest network (i.e., the end-state network) based on the modularity maximization criterion \cite{newman2006}.

<!--We investigate whether there are systematic cross-lingusitc variations in the order of aquisition of words that make up this vocabulary, and crucially, whether such variation influences the induced conceptual organization at different points in time. In fact, differences in the order of acqusition of words do not necessarily give rise to different conceptual organization. Imagine that two languages vary in whether "cow" or "dog" is acquired first. This difference will not change the induced conceptual organization across time since both "dog" and "cow" are instances of the same high-level concept "animal". -->

<!--## Features
We used two sources of information which represent two ways words may be related to one another in the semantic network. The first source was the MacRae features (McRae et al., 2005). These features were collected by giving adult participants a set of nouns and prompting them to provide various kinds of properties (perceptual, functional, encyclopedic, and taxonomic). We followed Hills et al. 2010 in excluding the encyclopedic and taxonomic properties as their role may not be important at this stage of development. The other source was the semantic similarity derived based on co-occurrence in the corpus of CHILDES, using word2vec.
-->

<!--
## Small World properties
We test whether the networks display the so-called "small-world" properties similar to other semantic and real-world networks (Steyvers & Tenenbaum, 2005; Watts & Strogatz, 1998). Small world properties are characterized with the average clustering coefficient $C$ and the average shortest path $L$. The former measures the extent to which the network is clustered, i.e., made of highly connectned sub-networks, whereas the latter measures the typical separation between tow nodes in the network. A network is small-word if it has a higher clustering coeffient comapred to a randomly connected network of the same size $C \gg C_{random}$, while still having a shorest path length as small as the one typically observed in random networks, that is $L \approx L_{random}$. 
-->

<!--Both Precison and Recall converge to 1 (perfect score) as $\mathcal{C}_t$ becomes more and more similar to $\mathcal{C}^*$. If precision starts low before converging to 1 (as opposed to being a constant at 1), this pattern would indicate that some pairs that should be differentiated are initially lumped together, suggesting a process of "differentiation" over development. Similarly, if we observe an increase in Recall, this pattern would indicate that some pairs that should be associated are initially differentiate, suggesting a process of "coelescence" over development. -->

## Learning mechanisms

We examined how higher-order concepts develop under the children's real word learning trajectory. We compared this development to the development induced by an exploration- and an exploitation-like learning. To construct the real word learning trajectory, we used the normative age of acquisition, that is, the age at which a word is produced by at least 50% of children in each language \cite{goodman2008}.

The exploration-based learning was instantiated as a uniform sampling from the end-state vocabulary. The exploitation-based learning had the additional constraint of sampling from one category at a time: the first word is selected randomly from one cluster, subsequent words are sampled from the same cluster. After all words from this cluster are used, a word from a different cluster is chosen, and the same process is repeated until all clusters are covered.\footnote{Note that the way we instantiated the exploitation-based learning is not fully unsupervised, but we were more interested in modeling extreme cases to which real learning can be compared.}
<!--
Since we are interested in the cross-linguistic study of development, we started by investigating the degree to which languages vary in their normative order of word learning. To this end, we calulated the pairwise Kendall rank correlation coefficient between languages, and we comapre it to the same measure obtained by comparing trajectories in different languages to random orderings.  The corresponding distributions, shown in Figure XX, do not overlap indicating that languages are more similar to each other than to random word orderings. The between-language distribution also shows there to be susbtantial cross-linguitc variability since the values are smaller than 1 (i.e., perfect correlation).
-->

<!--
```{r fig.env = "figure", fig.pos = "H", fig.align = "center", set.cap.width=T, fig.width=3, fig.height=4, num.cols.cap=2, fig.cap = "bla bla"}

@@

ggplot(cor_all, 
      aes(x = tau, fill=data)) +
  geom_histogram(aes(y = (..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
                 alpha=0.5,
                 binwidth=0.05)+
  #scale_x_log10() +
  theme_few() + 
  theme(legend.title = element_blank(),
      legend.text=element_text(size=7.5),
      axis.text = element_text(size = 7.5),
      strip.text = element_text(size = 7.5),
      axis.title = element_text(size = 7.5),
      aspect.ratio = 0.7
      )  +  #facet_grid(Segmentation ~ language)+
  scale_y_continuous(labels = scales::percent)+
  xlab("pairwise correlation") +ylab("Count") +
  theme(legend.position="bottom")

```
-->
# Results

```{r hi}
#Models

#m1_precision <- lmer(value ~ age *  randomization + (age *  randomization | language) + (1 | n_clusters),
#           data = subset(all, measure =='pair_precision_to_last' & randomization != "random_aoa"),
#          control=lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

#saveRDS(m1_precision, "model_1.rds")
#xl_precision <- readRDS("model_1.rds")

#m2_precision <- lmer(value ~ age *  randomization + (age *  randomization | language) + (1 | n_clusters),
#           data = subset(all, measure =='pair_precision_to_last' & randomization != "within_last_clustering"),
#           control=lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 1000000)))

#saveRDS(m2_precision, "model_2.rds")
#xp_precision <- readRDS("model_2.rds")

##Test of convergence
#relgrad <- with(xp_precision@optinfo$derivs,solve(Hessian,gradient))
#max(abs(relgrad))

#xl_recall <- lmer(value ~ age *  randomization + (age *  randomization | language) + (1 | n_clusters),
#           data = subset(all, measure =='pair_recall_to_last' & randomization != "random_aoa"),
#                     control=lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

#saveRDS(xl_recall, "xl_recall.rds")
#xl_recall <- readRDS("xl_recall.rds")

#m2_recall <- lmer(value ~ age *  randomization + (age *  randomization | language) + (1 | n_clusters),
#           data = subset(all, measure =='pair_recall_to_last' & randomization != "within_last_clustering"),
#          control=lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 1000000)))

#saveRDS(m2_recall, "model_recall_2.rds")
#xp_recall <- readRDS("model_recall_2.rds")

#relgrad <- with(xp_recall@optinfo$derivs,solve(Hessian,gradient))
#max(abs(relgrad))

#xl_prec_coef <- tibble::rownames_to_column(as.data.frame(coef(summary(xl_precision))), "effect") %>%
#  mutate(sampling = "exploitation", score = "precision")
#xp_prec_coef <- tibble::rownames_to_column(as.data.frame(coef(summary(xp_precision))), "effect") %>%
#  mutate(sampling = "exploration", score = "precision")
#xl_recall_coef <- tibble::rownames_to_column(as.data.frame(coef(summary(xl_recall))), "effect") %>%
#  mutate(sampling = "exploitation", score = "recall")
#xp_recall_coef <- tibble::rownames_to_column(as.data.frame(coef(summary(xp_recall))), "effect") %>%
#  mutate(sampling = "exploration", score ="recall")

#coef_all <- xl_prec_coef %>%
#  bind_rows(xp_prec_coef) %>%
#  bind_rows(xl_recall_coef) %>%
#  bind_rows(xp_recall_coef)

#feather::write_feather(coef_all, "../saved_data/coef_all.feather")
coef_all <- feather::read_feather("../saved_data/coef_all.feather")

p_val <- function(val) {
  if(val < 0.001) 
    {'< 0.001'} 
  else if(val < 0.01)
    {'<0.01'} 
  else if(val < 0.05)
    {'<0.05'} 
  else {paste('=', round(val,2))}
}

#Age 
age_xl_prec_co <- round(coef_all$Estimate[which(coef_all$effect=="age" &
                                                  coef_all$sampling=="exploitation" &
                                                  coef_all$score =="precision")],2)

age_xp_prec_co <- round(coef_all$Estimate[which(coef_all$effect=="age" &
                                                  coef_all$sampling=="exploration" &
                                                  coef_all$score =="precision")],2)

age_xl_rec_co <- round(coef_all$Estimate[which(coef_all$effect=="age" &
                                                  coef_all$sampling=="exploitation" &
                                                  coef_all$score =="recall")],2)

age_xp_rec_co <- round(coef_all$Estimate[which(coef_all$effect=="age" &
                                                  coef_all$sampling=="exploration" &
                                                  coef_all$score =="recall")],2)

age_xl_prec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="age" &
                                                  coef_all$sampling=="exploitation" &
                                                  coef_all$score =="precision")]

age_xp_prec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="age" &
                                                  coef_all$sampling=="exploration" &
                                                  coef_all$score =="precision")]

age_xl_rec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="age"  &
                                                  coef_all$sampling=="exploitation" &
                                                  coef_all$score =="recall")]

age_xp_rec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="age" &
                                                  coef_all$sampling=="exploration" &
                                                  coef_all$score =="recall")]

#Real vs. exploration

diff_xl_prec_co <- round(coef_all$Estimate[which(coef_all$effect=="randomizationwithin_last_clustering" &
                                                  coef_all$sampling=="exploitation" &
                                                  coef_all$score =="precision")],2)

diff_xp_prec_co <- round(coef_all$Estimate[which(coef_all$effect=="randomizationrandom_aoa" &
                                                  coef_all$sampling=="exploration" &
                                                  coef_all$score =="precision")],2)

diff_xl_rec_co <- round(coef_all$Estimate[which(coef_all$effect=="randomizationwithin_last_clustering" &
                                                  coef_all$sampling=="exploitation" &
                                                  coef_all$score =="recall")],2)

diff_xp_rec_co <- round(coef_all$Estimate[which(coef_all$effect=="randomizationrandom_aoa" &
                                                  coef_all$sampling=="exploration" &
                                                  coef_all$score =="recall")],2)

diff_xl_prec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="randomizationwithin_last_clustering" &
                                                  coef_all$sampling=="exploitation" &
                                                  coef_all$score =="precision")]

diff_xp_prec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="randomizationrandom_aoa" &
                                                  coef_all$sampling=="exploration" &
                                                  coef_all$score =="precision")]

diff_xl_rec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="randomizationwithin_last_clustering" &
                                                  coef_all$sampling=="exploitation" &
                                                  coef_all$score =="recall")]

diff_xp_rec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="randomizationrandom_aoa" &
                                                  coef_all$sampling=="exploration" &
                                                  coef_all$score =="recall")]

@@

Figure \ref{fig:results} shows the scores obtained through comparing $\mathcal{C}^*$ to $\mathcal{C}_t$ at different points in time $t$. For the real word learning trajectory, both precision and recall start relatively low, indicating that the induced conceptual organization is initially quite different from that of the end-state.  Both measures converge towards 1 (i.e., perfect score) as $\mathcal{C}_t$ becomes more and more similar to $\mathcal{C}^*$.

We first compared the real conceptual development to the one induced by exploration-based learning. To this end, we fit a mixed-effect regression using age and learning (real vs. exploration-based) as fixed effects, and using language and number of fixed clusters as random effects accounting for the nested structure of the data. Real and exploration-based patterns of conceptual developmental were indistinguishable for both precision ($\beta =$ `r diff_xp_prec_co`, $p$ `r p_val(diff_xp_prec_p)`) and recall ($\beta =$ `r diff_xp_rec_co`, $p$ `r p_val(diff_xp_rec_p)`).

Similarly, we compared real conceptual development to exploitation-based learning. Using a similar regression, we found a difference in both precision ($\beta =$ `r diff_xl_prec_co`, $p$ `r p_val(diff_xl_prec_p)`) and recall ($\beta =$ `r diff_xl_rec_co`, $p$ `r p_val(diff_xl_rec_p)`). Exploitation-base learning had generally higher precision, indicating there to be less false positive pairs. This result is due to the fact that we sampled instances from a same category. However, the same type of learning had lower recall, indicating there to be less false negative pairs. This second result was due to the fact that sampling from a same category leads to clusterings that are finer in their conceptual granularity than the end-state.

# Discussion

This paper asks whether children can learn abstract concepts based on word co-occurrence in the language they hear around them. We found that, when using co-occurrence information in the developing lexical network, several high-level concepts such as "animal", "artefact", "food" and "clothes" emerge bottom-up as clusters of highly inter-connected nodes. In addition, these categories develop simultaneously thanks to the children's word learning trajectory which tends to favor the exploration of the global conceptual landscape rather than the exploitation and refinement of one specific category at time.

The development of the higher-level conceptual structure seems to be unaffected by the order with which words are acquired (as long as this order approximates a uniform/exploration-like sampling), suggesting that the process of conceptual development can accommodate a wide range of word learning trajectories without qualitative change in the higher order organization. For example, whether acquisition start first with the words "cat" and "banana" or with the words "cow" and "potato" does not qualitatively affect the higher-level organization involving "animal" and "food". This property is important as it suggests, for instance, that development may be resilient to variability in the children's linguistic input \cite{slobin2014,hart1995}.

Developmental changes were captured by precision and recall. The increase in precision means that false positives decrease over time: some word pairs that are initially lumped together in a same category, are eventually differentiated. Similarly, the increase in recall means that false negatives decrease, that is, some word pairs that are initially distinct, become eventually subsumed by a same category. These patterns suggest a process of conceptual reorganization involving both "differentiation" and "coalescence" as was suggested in the developmental literature \cite{carey2009}.

That said, these developmental changes were not necessarily related to specific concepts (since the patterns were similar when we randomized the order of word learning). Instead, this finding suggests that differentiation and coalescence of word pairs in our data are related to the change in the vocabulary size across development: As more words are added to their lexical network, learners may approximate better the underlying conceptual organization of the mature lexicon, and would make less categorization errors. Indeed, research in network science indicates that properties of a real networks become more distorted as the size of a sampled sub-network decreases \cite{leskovec2006}.

One limitation of this study is that we used the normative age of acquisition, computed using different children at different age groups. This choice was due to the cross-sectional nature of available CDI data. Though such a measure has been widely used to study important aspects of the early lexical network \cite{hills2009,stella2017,storkel2009}, it only applies at the population level. In our case, though we found that average concept development is driven more by an exploration-based mechanism, some individual children may display an exploitation-like behavior. For example, prior knowledge about dinosaurs may enable the learning of new dinosaur-related words more easily \cite{chi1983}.

In sum, this work provided a quantitative account of how abstract concepts can emerge from the interaction of the children's learning mechanism and the properties of their linguistic input. One important direction for future work is to investigate the extent to which the correlational findings obtained in this study (e.g., the identity of categories formed across development or the fact that categorization errors decrease with the size of the lexicon) can be corroborated by controlled behavioral experiments.

<!--

leading to gradual improvements in the approximation of the underlying conceptual organization. More precisely, words are placed in a same cluster if they are more similar to one another than to words in a different clusters. However, this *relative* similarity depends on the existing items and their number. In particular, the larger the vocabulary, the better learners can approximate the underlying relative simialrity distribution of the mature lexicon, and the less categorization errors they make.

We compare the developmental patterns obtained with the normative trajectory to those obtained with the random trajectory. We demonstrated above that these trajectories are not correlated (Figure XX). Therefore, a priori it could have been the case that the normative trajectory has effects on higher-level conceptual organization above and beyond the effects induced by the random trajectory. Instead, Figure XX shows that the precsion and recall scores are strikingly similar in both trajectories across development. Thus, high level conceptual organizaton is quite robust to the order of word acquisition. To illustrate, acquisition may start with the word "dog" or with the word "cat", but this difference in the order of acquisition will not affect the induced super-ordinate category "animal".

<!--

We investigte whether the real conceptual development resembles more a pattern of exploitation- and exploration-based sampling.

The real word leanrining trajectory induces a conceptual organization which starts different from the end-state (lower precion and recall scores), and which becomes increasingly similar to the end-state

The results are shown for the real trajectory, as well

First we compare the trajectory of word learning to the trajectories that result from the two sampling mechanisms. Second, we examine the extent to which these trajectories induce different patterns of conceptual development.

Results are shown in Figure XX. We used mixed-effect linear regressions to examine how the trajectory of word learning compares to the two sampling mechanisms in the way they influence conceptual development.

Furthermore, the fact that normative and random trajectories have almost identical effects on the higher-level organization suggests that the observed developmental patterns (i.e., differentiation and coalescence of pairs of words) are not due to some specific order in word acquisition. Rather, they are due to the increase in the vocabulary size across development, leading to gradual improvements in the approximation of the underlying conceptual organization. More precisely, words are placed in a same cluster if they are more similar to one another than to words in a different clusters. However, this *relative* similarity depends on the existing items and their number. In particular, the larger the vocabulary, the better learners can approximate the underlying relative simialrity distribution of the mature lexicon, and the less categorization errors they make.

Next, we compare the normative and category-based learning (why?). Precsion is higher in the category-based trajectory, especially for earlier months. In contrast, the recall is lower. This pattern is due to the fact that learning is assumed to proceed based on conceptual similarity, e.g., if learning starts with an animal, then the next word will also be an animal. This learning produces less false postives because it samples instances from the same category (hence the high precison). Nevertheless, it also produces more false negative because it creates categories that are finer in their conceptual granualrity than the end-state (hence the low recall).

# Conclusion
This results suggests that real (normative) learning influences early conceptual development in a way that mimics random sampling and contrasts with category-based sampling. This suggests that early word learning favors exploration of the entire conceptual domain, rath

<!--
thus favoring exploration and which differ from category-based sampling.

conceptual development show different properties when word learning deviate

learning proceeds according to a similarity principle which sample words from the same category.

In contrast, the recall is lower. Category-based trajectory does not show a clear differentia

Finally, mixed effects model and cross-linguistic discussion,....

more frequent it is to approximate the end-state organization and to misplace words in . This phenomenon is similar to

The similarity of the scores in both trajectories also indicate that the increase in precision are recall are more likely due to small sample size, similar to the fact that a small size will not lead to prcise distribution,....

If we picture a word learning trajectory as way one could samples words from the end-state vocabulary, then random ordering corresponds to sparse sampling,

to the ones obtained with the randomly ranked trajectory. As shown in Figure XX, precision and recall scores in both trajectories are strinkingly similar across development. Thus, despite the fact that languages share some pattern of acquisition above and beyond chance (see Figure, XX), these shared patterns do not influence the higher level organizaton of these words. For example,

Investigation of the random trajectory allows us to understand whether the developmental patterns are specific to

@@

If precision is lower early on, it means that initial concepts are not differentiated enough, that is, pairs that should belong to different concpets are intially lamped together (false positives), despite the fact that we forced the same number of clsuters in both $\mathcal{C}_t$ and $\mathcal{C}^*$ (Why is this the case? This looks like an artefact of the clustering algorithm with smaller size data? Should discuss this with Isaac. Also, what is an exmaple of a clustering $\mathcal{C}_t$ for a smaller size: are some clusters totally empty?)

-->
